---
title: "Volleymetrics Code"
format: pdf
editor: visual
---

# Reception Statistic Analysis

## Functions List

### find_rec_player_report

Input a player name and it will provide a data frame of the players average pass rating based off of where they pass the ball from.

### find_rec_team_report

Input a team name and it will provide a data frame of all the players and their average pass rating based off of where they pass the ball from.

### Team_Win_Point_Percentage_By_Pass

Input a team name and it will provide a list of the % chance of winning a point based off of the pass rating.

## Pass Reception Startup

```{r}

library(tidyverse)
library(dplyr)
library(datavolley)
?datavolley
match <- dv_read("Beck_Zimmerman_MSU-IOWA.vsm")
match

stress <- match$plays |> mutate(difference_points)


```

```{r}

library(tidyverse)
match_data
match_data <- match$plays
match
all_receptions <- match_data |> filter(skill == "Reception") |>
  mutate(pass_rating = case_match(evaluation_code,
    "#" ~ 4,
    "+" ~ 3,
    "!" ~ 2,
    "-" ~ 1,
    "/" ~ 0,
    "=" ~ 0,
    .default = NA
  )) |> select(player_number, player_name, team, skill, skill_subtype, point_won_by, pass_rating)

all_receptions

passer_rating_by_player_num <- all_receptions |> group_by(player_number, player_name, team) |>
  summarize(average_pass_rating = mean(pass_rating))
  

passer_rating_by_player_num

```

## Passing Rating of Team

```{r}

avg_pass_rtg_by_team <- all_receptions |> group_by(team) |>
  summarize(avg_pass_rating = mean(pass_rating)) |>
  mutate(wl = case_match(team,
                         "Michigan State University" ~ 1,
                         "University of Iowa" ~ 0))

avg_pass_rtg_by_team

```

## Reading all the match data in

```{r}

filenames <- c(
" Beck_Zimmerman_PSU-PITT.vsm", 
"Anika_Malapati_IND-BRA.vsm", 
"Anika_Malapati_IOWA-UW.vsm", 
"Anika_Malapati_NW-NEB.vsm", 
"Anika_Malapati_OSU-Ohio.vsm", 
"Anika_Malapati_PSU-MSU.vsm", 
"Anika_Malapati_PSU-UK.vsm",
"Anika_Malapati_PU-SMU.vsm",
"Anika_Malapati_RUT-MSU.vsm",
"Anika_Malapati_RUT-UMICH.vsm",
"Anika_Malapati_STA-UT.vsm",
"Anika_Malapati_UMICH-OSU.vsm",
"Anika_Malapati_UMN-MSU.vsm",
"Anika_Malapati_UMN-RU.vsm",
"Anika_Malapati_UTEP-TAMUCC.vsm",
"Anika_Malapati_UTEP-UCD.vsm",
"Anika_Malapati_UW-Madison-UMD.vsm",
"Anika_Malapati_UW-NW.vsm",
"Anika_Malapati_UW-PSU.vsm",
"Anika_Malapati_UW-USC.vsm",
#"Beck_Zimmerman_BAL-PUR.vsm",
"Beck_Zimmerman_ILL-PSU.vsm",
#"Beck_Zimmerman_MEM-TSU.vsm",
"Beck_Zimmerman_MICH_IOWA.vsm",
"Beck_Zimmerman_MICH-MSU.vsm",
"Beck_Zimmerman_MSU-IOWA.vsm",
"Beck_Zimmerman_MSU-UMD.vsm",
"Beck_Zimmerman_NU-IU.vsm",
"Beck_Zimmerman_ORE-UMN.vsm",
"Beck_Zimmerman_ORE-WISC.vsm",
"Beck_Zimmerman_OSU-RU.vsm",
"Beck_Zimmerman_PEP-UCD.vsm",
#"Beck_Zimmerman_PEP-UTP.vsm",
#"Beck_Zimmerman_PSU-CMU.vsm",
"Beck_Zimmerman_PSU-PRIN.vsm",
"Beck_Zimmerman_STA-UF.vsm",
"Beck_Zimmerman_STAN-DAVIS.vsm",
#"Beck_Zimmerman_STAN-USU.vsm",
"Beck_Zimmerman_TSU-UTEP.vsm",
"Beck_Zimmerman_UH-PORT.vsm",
"Beck_Zimmerman_UMD-RU.vsm",
#"Beck_Zimmerman_UOH-UVU.vsm",
"Beck_Zimmerman_USC-PURD.vsm",
"Beck_Zimmerman_UW-MSU.vsm",
"Beck_Zimmerman_UW-UMN.vsm",
#"Beck_Zimmerman_WISC-MICH.vsm",
"Brandon_Wong_STA-ORE.vsm",
"Ethan_Rome_IU-NU.dvw",
"Ethan_Rome_NU-UI.dvw",
"Ethan_Rome_OSU-UF.dvw",
"Ethan_Rome_OSU-WSU.dvw",
"Ethan_Rome_OU-UW.dvw",
"Ethan_Rome_PSU-UW.dvw",
"Ethan_Rome_PUR-UW.dvw",
"Ethan_Rome_TCU-PITT.dvw",
"Ethan_Rome_TSU-ASU.dvw",
"Ethan_Rome_UIUC-UW.dvw",
"Ethan_Rome_UMN-UNL.dvw",
"Ethan_Rome_UNL-STA.dvw",
"Ethan_Rome_UO-UMICH.dvw",
"Ethan_Rome_UTEP-UTRGV.dvw",
"Ethan_Rome_UW-UIUC.dvw",
"Ethan_Rome_UWM-USC.dvw",
"Ethan_Rome_WKU-IU.dvw",
"Ethan_Rome-IU-UW.dvw",
"Grace_Palumbo_MARY-UIUC.vsm",
"Grace_Palumbo_MARY-WISC.vsm",
"Grace_Palumbo_MICH-MIN.vsm",
"Grace_Palumbo_ORE-IOWA.vsm",
"Grace_Palumbo_OSU-TROY.vsm",
"Grace_Palumbo_OSU-USC.vsm",
"Grace_Palumbo_OSU-UVA.vsm",
"Grace_Palumbo_PSU-TCU.dvw",
"Grace_Palumbo_RUT-OSU.vsm",
"Grace_Palumbo_TSU-TULSA.vsm",
"Grace_Palumbo_UH-PORT.vsm",
"Grace_Palumbo_UH-SJU.vsm",
"Grace_Palumbo_UM-STA.vsm",
"Grace_Palumbo_UNL-UIUC.vsm",
"Grace_Palumbo_UO-PSU.vsm",
"Grace_Palumbo_UW-WISC.vsm",
"2025-12-04 UCLA-GT.dvw",
"2025-09-20 UCLA-UH.dvw",
"2025-09-19 UCLA-TXSU.dvw",
"2025-10-08 UCLA-MIN.dvw",
"2025-10-22 UCLA-ORE.dvw",
"2025-09-02 UCLA-PEPP.dvw",
"2025-09-11 UCLA-UTEP.dvw",
"2025-09-28 UCLA-PSU.dvw",
"2025-09-26 UCLA-OSU.dvw",
"2025-10-11 UCLA-USC.dvw",
"2025-11-20 UCLA-ILL.dvw",
"2025-09-05 UCLA-TCU.dvw",
"2025-11-28 UCLA-MSU.dvw",
"2025-10-25 UCLA-MAR.dvw",
"2025-11-08 UCLA-NU.dvw",
"2025-10-17 UCLA-WIS.dvw",
"2025-09-13 UCLA-TSU.dvw",
"2025-09-21 UCLA-STA.dvw",
"2025-11-26 UCLA-UM.dvw",
"2025-09-06 UCLA-TCU.dvw",
"2025-11-14 UCLA-UNL.dvw",
"2025-12-05 UCLA-UK.dvw",
"2025-11-15 UCLA-Rut.dvw",
"2025-11-02 UCLA-UW.dvw",
"2025-09-12 UCLA-ORU.dvw",
"2025-10-02 UCLA-PUR.dvw",
"2025-09-01 UCLA-CSULB.dvw",
"2025-11-06 UCLA-ORE.dvw",
"2025-11-22 UCLA-UW.dvw",
"2025-10-04 UCLA-IU.dvw"
)


list_of_matches <- lapply(filenames, dv_read)

match_outcomes <- bind_rows(lapply(list_of_matches,
                                  function(x){
                                    x$meta$teams |>
                                      mutate(match_id = x$meta$match_id) |>
                                      dplyr::select(match_id, team, won_match)
                                  }))

all_match_data <- bind_rows(lapply(list_of_matches, function(x) {
  x$plays |>
    mutate(match_id = x$meta$match_id)
}))

all_matches_outcomes <- all_match_data |> left_join(match_outcomes, by = c("match_id", "team"))

write.csv(all_matches_outcomes, "all_matches_outcomes.csv")

```

## Reception Analysis Function

```{r}


all_match_receptions <- all_matches_outcomes |>
  filter(skill == "Reception") |>
  mutate(pass_rating = case_match(evaluation_code,
    "#" ~ 4,
    "+" ~ 3,
    "!" ~ 2,
    "-" ~ 1,
    "/" ~ 0,
    "=" ~ 0,
    .default = NA
  ), win_loss = if_else(won_match, 1, 0)) |> 
  dplyr::select(player_number, player_name, team, skill, skill_subtype, point_won_by, pass_rating, win_loss)

all_pass_rtg_by_win <- all_match_receptions |> filter(win_loss == 1) |>
  summarize(avg_pass_rating = mean(pass_rating))

all_pass_rtg_by_loss <- all_match_receptions |> filter(win_loss == 0) |>
  summarize(avg_pass_rating = mean(pass_rating))

avg_pass_rtg_by_team <- all_match_receptions |> group_by(team, win_loss) |>
  summarize(avg_pass_rating = mean(pass_rating))




reception_by_location <- all_match_receptions |> group_by(skill_subtype) |>
  summarize(avg_pass_rating = mean(pass_rating))
reception_by_location

reception_by_player_by_location <- all_match_receptions |> group_by(player_number, player_name, skill_subtype, team) |>
  summarize(avg_pass_rating = mean(pass_rating, na.rm = TRUE), .groups = "drop")
reception_by_player_by_location

rec_low_ranked <- reception_by_player_by_location |> filter(skill_subtype == "Low") |>
  arrange(desc(avg_pass_rating))
rec_low_ranked

find_rec_player_report <- function(x) {
  
  reception_by_player_by_location |> filter(player_name == x) |> 
    dplyr::select(player_name, skill_subtype, avg_pass_rating) |>
  arrange(desc(avg_pass_rating))
  
}

find_rec_player_report("Anna Pringle")

cat("Teams that win matches have an average pass rating of", as.numeric(all_pass_rtg_by_win), ".\n")

cat("Teams that lose matches have an average pass rating of", as.numeric(all_pass_rtg_by_loss), ".\n")

cat("This results in a difference of", as.numeric(all_pass_rtg_by_win) - as.numeric(all_pass_rtg_by_loss), "average passer rating.", "\n")


```

## Player Reception Location Function and by team option

```{r}

find_rec_player_report <- function(x) {
  
  reception_by_player_by_location |> filter(player_name == x) |> 
    dplyr::select(player_name, skill_subtype, avg_pass_rating) |>
  arrange(desc(avg_pass_rating))
  
}

find_rec_player_report("Adonia Faumuina")

find_rec_team_report <- function(x) {
  
  reception_by_player_by_location |> filter(team == x) |> 
    dplyr::select(team, player_number, player_name, skill_subtype, avg_pass_rating) |>
  arrange(desc(avg_pass_rating))
  
}

find_rec_team_report("University of Southern California")

all_match_receptions_pass_totals <- all_match_receptions |> 
  group_by(player_name) |> 
  mutate(total_passes = n()) |> 
  filter(total_passes >= 20) |>
  summarize(avg_pass_rating = mean(pass_rating, na.rm = TRUE))

all_match_receptions |> 
  group_by(player_name) |> 
  mutate(total_passes = n()) |>
  filter(team == "University of Southern California")
  
reception_by_player_by_location
all_match_receptions_pass_totals |> arrange(desc(avg_pass_rating))


reception_by_player_by_location |> filter(skill_subtype == "Overhand") |> arrange(desc(avg_pass_rating))

```

## Point Won or Lost by pass rating Analysis

```{r}

# count of 0 pass rated
pass_0 <- all_match_receptions |> filter(pass_rating == 0)
pass_0 <- nrow(pass_0)

# count of 1 pass rated
pass_1 <- all_match_receptions |> filter(pass_rating == 1)
pass_1 <- nrow(pass_1)

# count of 2 pass rated
pass_2 <- all_match_receptions |> filter(pass_rating == 2)
pass_2 <- nrow(pass_2)

# count of 3 pass rated
pass_3 <- all_match_receptions |> filter(pass_rating == 3)
pass_3 <- nrow(pass_3)

# count of 4 pass rated
pass_4 <- all_match_receptions |> filter(pass_rating == 4)
pass_4 <- nrow(pass_4)

# pass total
pass_total <- nrow(all_match_receptions)

# adding column of 1 or 0 for yes or no the team that passed won the point
pass_rating_point_wol <- all_match_receptions |>
  mutate(won_point = ifelse(point_won_by == team, 1, 0))

# pass rating 0 win loss percentage
pass_rating_point_0_won <- pass_rating_point_wol |>
  filter(pass_rating == 0, won_point == 1)

total_points_won_0 <- nrow(pass_rating_point_0_won)

total_pts_won_per_0 <- total_points_won_0 / pass_0
total_pts_won_per_0

for (i in 0:4) {
  
  pass_i <- all_match_receptions |> filter(pass_rating == i)
  pass_i <- nrow(pass_i)
  
  pass_rating_point_i_won <- pass_rating_point_wol |>
  filter(pass_rating == i, won_point == 1)
  
  total_points_won_i <- nrow(pass_rating_point_i_won)
  total_pts_won_per_i <- round((total_points_won_i / pass_i) * 100, digits = 2)
  
  cat(total_pts_won_per_i, "% chance of winning the point with a ", i, " pass rating", "\n", sep = "")
  
}

```

## Function to find % point is won by passing rating by team

```{r}

Team_Win_Point_Percentage_By_Pass <- function(x) {
  
  pass_rating_point_wol_team <- pass_rating_point_wol |> filter(team == x)
  
  all_match_receptions_team <- all_match_receptions |> filter(team == x)
  
  for (i in 0:4) {
  
  pass_i <- all_match_receptions_team |> filter(pass_rating == i)
  pass_i <- nrow(pass_i)
  
  pass_rating_point_i_won <- pass_rating_point_wol_team |>
  filter(pass_rating == i, won_point == 1)
  
  total_points_won_i <- nrow(pass_rating_point_i_won)
  total_pts_won_per_i <- round((total_points_won_i / pass_i) * 100, digits = 2)
  
  cat(total_pts_won_per_i, "% chance of winning the point with a ", i, " pass rating", "\n", sep = "")
  
}
  
}

Team_Win_Point_Percentage_By_Pass("Pennsylvania State University")

```
## NEW OFFENSIVE STATISTIC

```{r}

all_attacks <- all_matches_outcomes |> filter(skill == "Attack")

all_attacks_grouped <- all_attacks |> group_by(player_name) |>
  mutate(total_hits = n()) |> 
  ungroup() |> 
  filter(total_hits >= 25) |>
  dplyr::select(team, player_number, player_name, skill_type, evaluation_code, evaluation, attack_code, attack_description, skill_subtype, num_players_numeric, phase, total_hits) |>
  mutate(attack_rating = case_match(evaluation_code,
    "#" ~ 3,
    "+" ~ 2,
    "-" ~ 1,
    "/" ~ 0,
    "=" ~ 0,
    .default = NA
  )) |> dplyr::select(-evaluation_code, -evaluation, -skill_type, -skill_subtype) |>
  mutate(block_rating = case_match(num_players_numeric,
    4 ~ 0,
    3 ~ 3,
    2 ~ 2,
    1 ~ 1,
    0 ~ 0,
    .default = NA
  )) |>
    mutate(rec_tran_phase_diff_score = case_match(phase,
    "Reception" ~ 1,
    "Transition" ~ 1.5,
    .default = NA
  )) |> 
  mutate(diff_score = rec_tran_phase_diff_score * block_rating) |>
  mutate(new_offensive_strength_stat = (attack_rating + 1) / (diff_score + 1))

all_attacks_grouped

kennedy_martin_attacks <- all_attacks_grouped |> filter(player_name == "Kennedy Martin") |>
  drop_na() |>
  mutate(OSS = mean(new_offensive_strength_stat)) |>
  dplyr::select(team, player_number, player_name, total_hits, OSS) |>
  slice(1)

player_attack_score <- function(player) {
  
  player_attacks <- all_attacks_grouped |> filter(player_name == player) |>
  drop_na() |>
  mutate(OSS = mean(new_offensive_strength_stat)) |>
  dplyr::select(team, player_number, player_name, total_hits, OSS) |>
  slice(1)
  return(player_attacks)
  
}

player_attack_score("Kennedy Martin")
player_attack_score("Olivia Babcock")
player_attack_score("Harper Murray")
player_attack_score("Andi Jackson")
player_attack_score("Carter Booth")

players <- c("Kennedy Martin", "Olivia Babcock", "Harper Murray", "Andi Jackson", "Carter Booth", "Emmi Sellman", "Tendai Titley", "Gentry Brown", "Staniszewska Karolina", "Mumcular Bianca")

player_stats <- players |> 
  map_dfr(player_attack_score)

print(player_stats)

all_attacks_OSS <- all_attacks_grouped |> group_by(player_name) |> drop_na() |> 
  mutate(OSS = mean(new_offensive_strength_stat)) |>
  dplyr::select(team, player_number, player_name, total_hits, OSS) |>
  distinct()
  
all_attacks_OSS

max(all_attacks_OSS$OSS)
min(all_attacks_OSS$OSS)

all_attacks_OSS |> filter(OSS == 3.02)
all_attacks_OSS |> filter(OSS < 1)

```

## Libero out of system efficiency

```{r}

# removing the double up attacks and combining the set and attacks together into the same line of code
all_match_set_attack <- all_match_data |> filter(skill == "Set" | skill == "Attack") |> filter(team == "Pennsylvania State University") |> filter(!(skill == "Attack" & lag(skill) == "Attack")) |>
  mutate(play_id = cumsum(skill == "Set")) |>
  pivot_wider(
    id_cols = c(video_file_number, play_id, team),
    names_from = skill,
    values_from = -c(video_file_number, play_id, team),
    names_glue = "{skill}_{.value}"
  )

# removing the setter from the calculations
all_match_set_attack_no_setter <- all_match_set_attack |> filter(Set_player_number != 7) |> dplyr::select(Set_player_number, Set_player_name, Attack_player_number, Attack_player_name, Attack_evaluation_code) |>
  mutate(attack_rating = case_match(Attack_evaluation_code,
    "#" ~ 1,
    "+" ~ 0,
    "-" ~ 0,
    "/" ~ -1,
    "=" ~ -1,
    .default = NA
  )) |> drop_na() |>
  group_by(Set_player_number) |>
  mutate(hitter_effiency = sum(attack_rating) / n()) |>
  mutate(number_sets = n()) |>
  ungroup()

# Compiling the table into a summary

setter_hitter_efficiency <- all_match_set_attack_no_setter |>
  group_by(Set_player_number, Set_player_name) |>
  summarize(
    hitter_effiency = sum(attack_rating) / n(),
    number_sets = n(),
    .groups = "drop"
  )

setter_hitter_efficiency

```




## Anika R Code





## Shiny Dashboard

```{r}

library(shiny)
library(tidyverse)
library(bslib) 

# ==========================================
# UI
# ==========================================
ui <- page_navbar(
  title = "Volleyball Analytics Dashboard",
  theme = bs_theme(version = 5, preset = "flatly"),
  
  # TAB 1: PLAYER & TEAM STATS
  nav_panel(title = "Serve Reception",
    layout_sidebar(
      sidebar = sidebar(
        selectInput("player_select", "Select Player for Report:", choices = NULL),
        helpText("Data pulled from global environment. Only players with >20 total passes shown.")
      ),
      
      layout_columns(
        col_widths = c(12, 12, 6, 6),
        card(card_header("Overall Match Passing Statistics"), uiOutput("win_loss_summary")),
        card(card_header("Average Pass Rating by Team"), tableOutput("team_averages")),
        card(card_header("Player Reception Report (By Location)"), tableOutput("player_report")),
        card(card_header("Overall Passer Rating Leaderboard"), tableOutput("overall_leaderboard"))
      )
    )
  ),
  
  # TAB 2: POINT WIN % BY PASS RATING
  nav_panel(title = "Point Win % Analysis",
    layout_sidebar(
      sidebar = sidebar(
        selectInput("team_select", "Select Team to Analyze:", choices = NULL),
        helpText("Analyze the probability of winning the point based on the pass rating.")
      ),
      
      layout_columns(
        col_widths = c(6, 6), 
        card(card_header("Overall (All Teams) % Chance to Win Point"), tableOutput("overall_point_win_pct")),
        card(card_header(textOutput("team_point_win_header")), tableOutput("team_point_win_pct"))
      )
    )
  ),
  
  # TAB 3: OFFENSIVE STRENGTH STAT (OSS)
  nav_panel(title = "Offensive Strength (OSS)",
    layout_sidebar(
      sidebar = sidebar(
        selectInput("oss_team_select", "Select Team Roster:", choices = NULL),
        helpText("Displays your custom Offensive Strength Stat (OSS). Factors in attack outcome, number of blockers, and game phase."),
        helpText(strong("Note: "), "Only includes players with 20 or more attacks.")
      ),
      
      layout_columns(
        col_widths = c(6, 6),
        card(
          card_header(textOutput("oss_team_header")),
          tableOutput("oss_team_table")
        ),
        card(
          card_header("Overall Match OSS Leaderboard"),
          tableOutput("oss_overall_table")
        )
      )
    )
  ),
  
  # TAB 4: OUT OF SYSTEM EFFICIENCY 
  nav_panel(title = "Out of System",
    layout_sidebar(
      sidebar = sidebar(
        selectInput("oos_team_select", "Select Team:", choices = NULL),
        helpText("Analyzes the hitting efficiency of attackers based on who set them the ball."),
        helpText(strong("Note: "), "Only displays players with 10 or more sets. The player with the highest volume per team is marked as the Primary Setter.")
      ),
      
      card(
        card_header(textOutput("oos_header")),
        tableOutput("oos_table")
      )
    )
  ),

  # TAB 5: SERVING ANALYSIS (SPI)
  nav_panel(title = "Serving (SPI)",
    layout_sidebar(
      sidebar = sidebar(
        selectInput("serve_team_select", "Select Team:", choices = NULL),
        helpText("Serve Performance Index (SPI): Ace (#) = +1.0, Good Pressure (+) = +0.5, Error (-) = -1.0. Higher is better."),
        helpText(strong("Note: "), "Player leaderboards only include servers with 20 or more serves. Zones are the server's start zone.")
      ),

      layout_columns(
        col_widths = c(6, 6, 6, 6),
        card(card_header(textOutput("serve_team_header")), tableOutput("serve_team_table")),
        card(card_header("Overall SPI Leaderboard"), tableOutput("serve_overall_table")),
        card(card_header(textOutput("serve_zone_header")), tableOutput("serve_zone_table")),
        card(card_header("SPI by Serve Zone"), plotOutput("serve_zone_plot"))
      )
    )
  ),

  # TAB 6: BLOCKING - OVERALL SUMMARY
  nav_panel(title = "Blocking (Overall)",
    layout_sidebar(
      sidebar = sidebar(
        helpText("Block Influence Score (BIS): Block Kill (#) = +1.0, Block Touch (+) = +0.5, Block Error (-) = -1.0."),
        helpText("Efficiency = (Kills - Errors) / Attempts. Touch Rate = share of blocks that win the point or stay in play."),
        helpText(strong("Note: "), "Player leaderboard only includes blockers with 10 or more block attempts.")
      ),

      layout_columns(
        col_widths = c(12, 12, 12),
        card(card_header("Overall Blocking Leaderboard (BIS)"), tableOutput("block_overall_table")),
        card(card_header("Team Blocking Summary"), tableOutput("block_team_summary")),
        card(card_header("Opponent Hitting % vs Block Presence (All Teams)"), tableOutput("block_impact_table"))
      )
    )
  ),

  # TAB 7: BLOCKING - SPECIFIC TEAM
  nav_panel(title = "Blocking (Team)",
    layout_sidebar(
      sidebar = sidebar(
        selectInput("block_team_select", "Select Team:", choices = NULL),
        helpText("Block Influence Score (BIS): Block Kill (#) = +1.0, Block Touch (+) = +0.5, Block Error (-) = -1.0."),
        helpText("Efficiency = (Kills - Errors) / Attempts. Touch Rate = share of blocks that win the point or stay in play."),
        helpText(strong("Note: "), "Player tables only include blockers with 10 or more block attempts.")
      ),

      layout_columns(
        col_widths = c(12, 6, 6),
        card(card_header(textOutput("block_team_header")), tableOutput("block_team_table")),
        card(card_header(textOutput("block_impact_team_header")), tableOutput("block_impact_team_table")),
        card(card_header(textOutput("block_eff_header")), plotOutput("block_eff_plot"))
      )
    )
  ),

  # ==========================================
  # PRESSURE / CLUTCH SITUATIONS (score >= 20)
  # ==========================================
  nav_menu(
    title = "Pressure / Clutch",

    # CLUTCH SERVING
    nav_panel(title = "Clutch Serving",
      layout_sidebar(
        sidebar = sidebar(
          selectInput("clutch_serve_team", "Select Team:", choices = NULL),
          helpText("Serves hit when either team has reached 20 points."),
          helpText(strong("Aggressive %"), "= Ace or Positive serves. ",
                   strong("Point-Scoring %"), "= rally won while serving.")
        ),
        layout_columns(
          col_widths = c(12, 12),
          card(card_header(textOutput("clutch_serve_header")), tableOutput("clutch_serve_team_table")),
          card(card_header("Clutch Serving Leaderboard (All Teams)"), tableOutput("clutch_serve_overall_table"))
        )
      )
    ),

    # CLUTCH RECEPTION
    nav_panel(title = "Clutch Reception",
      layout_sidebar(
        sidebar = sidebar(
          selectInput("clutch_rec_team", "Select Team:", choices = NULL),
          helpText("Receptions made when either team has reached 20 points."),
          helpText(strong("Good Pass %"), "= Perfect or Positive passes. ",
                   strong("Side-Out %"), "= rally won after passing.")
        ),
        layout_columns(
          col_widths = c(12, 12),
          card(card_header(textOutput("clutch_rec_header")), tableOutput("clutch_rec_team_table")),
          card(card_header("Clutch Reception Leaderboard (All Teams)"), tableOutput("clutch_rec_overall_table"))
        )
      )
    ),

    # CLUTCH OFFENSE
    nav_panel(title = "Clutch Offense",
      layout_sidebar(
        sidebar = sidebar(
          selectInput("clutch_off_team", "Select Team:", choices = NULL),
          helpText("Attacks taken when either team has reached 20 points."),
          helpText("Efficiency = (Kills - Errors - Blocked) / Attempts."),
          helpText(strong("Note: "), "Only includes players with 10 or more clutch attacks.")
        ),
        layout_columns(
          col_widths = c(12, 12),
          card(card_header(textOutput("clutch_off_header")), tableOutput("clutch_off_team_table")),
          card(card_header("Clutch Offense Leaderboard (All Teams)"), tableOutput("clutch_off_overall_table"))
        )
      )
    ),

    # ALL-AROUND CLUTCH
    nav_panel(title = "All-Around Clutch",
      layout_sidebar(
        sidebar = sidebar(
          helpText("Clutch Index combines all three skills in pressure situations:"),
          helpText("(Hitting Eff x 100) + Side-Out % + Serve Point-Scoring %."),
          helpText(strong("Note: "), "Only includes players with 15 or more total clutch touches.")
        ),
        layout_columns(
          col_widths = c(12, 12),
          card(card_header("Most Clutch Player on Each Team"), tableOutput("top_clutch_team_table")),
          card(card_header("Top 20 All-Around Clutch Players"), tableOutput("clutch_overall_table"))
        )
      )
    )
  ),

  # ==========================================
  # SERVE EFFICIENCY INDEX (SEI)
  # ==========================================
  nav_menu(
    title = "Serve Efficiency (SEI)",

    # SEI LEADERBOARD
    nav_panel(title = "SEI Leaderboard",
      layout_sidebar(
        sidebar = sidebar(
          selectInput("sei_team", "Select Team:", choices = NULL),
          helpText("SEI = (Win% x 0.5) + (Ace% x 0.3) + (OOS% x 0.2) - (Error% x 0.1)."),
          helpText("OOS% = serves that forced the opponent out of system."),
          helpText(strong("Note: "), "Only includes player/serve-type combos with 20 or more serves.")
        ),
        layout_columns(
          col_widths = c(12, 12),
          card(card_header(textOutput("sei_team_header")), tableOutput("sei_team_table")),
          card(card_header("Top SEI Servers (All Teams)"), tableOutput("sei_overall_table"))
        )
      )
    ),

    # SERVE TYPE COMPARISON
    nav_panel(title = "Serve Type Comparison",
      layout_sidebar(
        sidebar = sidebar(
          helpText("Season-long averages comparing Float, Jump, and Jump-Float serves across all games.")
        ),
        card(
          card_header("Advanced Serve Efficiency: Floaters vs. Jump Serves"),
          plotOutput("sei_type_plot", height = "520px")
        )
      )
    ),

    # SEI QUADRANT CHART
    nav_panel(title = "SEI Quadrant",
      layout_sidebar(
        sidebar = sidebar(
          helpText("Each point is a player's serve type (min 30 serves). Dashed lines are league averages."),
          helpText(strong("Top-left:"), " snipers (low error, high OOS)."),
          helpText(strong("Top-right:"), " heavy hitters (high risk, high reward)."),
          helpText(strong("Bottom-left:"), " safe servers (low risk, low OOS)."),
          helpText(strong("Bottom-right:"), " high risk, low reward.")
        ),
        card(
          card_header("Error % vs. Out-of-System %"),
          plotOutput("sei_quadrant_plot", height = "520px")
        )
      )
    )
  )
)

# ==========================================
# SERVER
# ==========================================
server <- function(input, output, session) {
  
  # ---------------------------------------------------------
  # REACTIVE DATA PREP
  # ---------------------------------------------------------
  
  # Tab 1: Reception Data
  player_totals <- reactive({
    req(exists("all_match_receptions", envir = .GlobalEnv))
    all_match_receptions |>
      group_by(player_name, team) |>
      summarize(total_passes = n(), overall_avg_rating = mean(pass_rating, na.rm = TRUE), .groups = "drop") |>
      filter(total_passes > 20)
  })
  
  # Tab 2: Point Win Data
  pass_rating_point_wol <- reactive({
    req(exists("all_match_receptions", envir = .GlobalEnv))
    all_match_receptions |>
      filter(!is.na(pass_rating)) |>
      mutate(won_point = ifelse(point_won_by == team, 1, 0))
  })
  
  # Tab 3: OSS Data
  oss_data <- reactive({
    req(exists("all_matches_outcomes", envir = .GlobalEnv))
    
    all_matches_outcomes |>
      filter(skill == "Attack") |>
      group_by(player_name, team) |>
      mutate(total_hits = n()) |>
      filter(total_hits >= 20) |> 
      ungroup() |>
      mutate(
        attack_rating = case_match(evaluation_code,
                                   "#" ~ 3,
                                   "+" ~ 2,
                                   "-" ~ 1,
                                   "/" ~ 0,
                                   "=" ~ 0,
                                   .default = NA
        ),
        block_rating = case_match(num_players_numeric,
                                  4 ~ 0,
                                  3 ~ 3,
                                  2 ~ 2,
                                  1 ~ 1,
                                  0 ~ 0,
                                  .default = NA
        ),
        rec_tran_phase_diff_score = case_match(phase,
                                               "Reception" ~ 1,
                                               "Transition" ~ 1.5,
                                               .default = NA
        )
      ) |>
      drop_na(attack_rating, block_rating, rec_tran_phase_diff_score) |> 
      mutate(
        diff_score = rec_tran_phase_diff_score * block_rating,
        new_offensive_strength_stat = (attack_rating + 1) / (diff_score + 1)
      ) |>
      group_by(team, player_number, player_name) |>
      summarize(
        total_hits = first(total_hits),
        OSS = mean(new_offensive_strength_stat, na.rm = TRUE),
        .groups = "drop"
      )
  })
  
  # Tab 4: Out of System Data
  oos_data <- reactive({
    req(exists("all_match_data", envir = .GlobalEnv))
    
    all_match_data |>
      filter(skill %in% c("Set", "Attack")) |>
      group_by(match_id, team) |> 
      filter(!(skill == "Attack" & lag(skill) == "Attack")) |>
      mutate(play_id = cumsum(skill == "Set")) |>
      ungroup() |>
      pivot_wider(
        id_cols = c(match_id, play_id, team),
        names_from = skill,
        values_from = c(player_number, player_name, evaluation_code),
        names_glue = "{skill}_{.value}"
      ) |>
      mutate(
        attack_rating = case_match(Attack_evaluation_code,
                                   "#" ~ 1,
                                   "+" ~ 0,
                                   "-" ~ 0,
                                   "/" ~ -1,
                                   "=" ~ -1,
                                   .default = NA
        )
      ) |>
      drop_na(attack_rating, Set_player_number) |>
      group_by(team, Set_player_number, Set_player_name) |>
      summarize(
        hitter_efficiency = sum(attack_rating) / n(),
        number_sets = n(),
        .groups = "drop"
      ) |>
      group_by(team) |>
      mutate(
        # Identify the primary setter dynamically by whoever has the max sets on the team
        Set_player_name = ifelse(number_sets == max(number_sets), 
                                 paste0(Set_player_name, " (Primary Setter)"), 
                                 Set_player_name)
      ) |>
      ungroup() |>
      filter(number_sets >= 10) # Enforce the minimum 10 sets threshold
  })
  
  # ---------------------------------------------------------
  # DYNAMIC UI UPDATES (Dropdowns)
  # ---------------------------------------------------------
  
  observe({
    req(player_totals())
    updateSelectInput(session, "player_select", choices = sort(unique(player_totals()$player_name)))
  })
  
  observe({
    req(pass_rating_point_wol())
    updateSelectInput(session, "team_select", choices = sort(unique(pass_rating_point_wol()$team)))
  })
  
  observe({
    req(oss_data())
    updateSelectInput(session, "oss_team_select", choices = sort(unique(oss_data()$team)))
  })
  
  observe({
    req(oos_data())
    updateSelectInput(session, "oos_team_select", choices = sort(unique(oos_data()$team)))
  })
  
  # ---------------------------------------------------------
  # TAB 1 OUTPUTS
  # ---------------------------------------------------------
  
  output$win_loss_summary <- renderUI({
    req(exists("all_match_receptions", envir = .GlobalEnv))
    df <- all_match_receptions
    avg_win <- df |> filter(win_loss == 1) |> summarize(avg = mean(pass_rating, na.rm = TRUE)) |> pull(avg)
    avg_loss <- df |> filter(win_loss == 0) |> summarize(avg = mean(pass_rating, na.rm = TRUE)) |> pull(avg)
    diff <- avg_win - avg_loss
    
    tagList(
      p(strong("Teams that win matches have an average pass rating of: "), round(avg_win, 3)),
      p(strong("Teams that lose matches have an average pass rating of: "), round(avg_loss, 3)),
      p(strong("This results in a difference of: "), round(diff, 3), " average passer rating.")
    )
  })
  
  output$team_averages <- renderTable({
    req(exists("all_match_receptions", envir = .GlobalEnv))
    all_match_receptions |>
      group_by(team, win_loss) |>
      summarize(avg_pass_rating = mean(pass_rating, na.rm = TRUE), .groups = "drop") |>
      arrange(desc(avg_pass_rating)) |>
      mutate(Rank = row_number()) |>
      mutate(win_loss = ifelse(win_loss == 1, "Win", "Loss")) |>
      relocate(Rank) |>
      rename(Team = team, `Match Outcome` = win_loss, `Average Pass Rating` = avg_pass_rating)
  }, digits = 3)
  
  output$player_report <- renderTable({
    req(exists("reception_by_player_by_location", envir = .GlobalEnv), input$player_select)
    reception_by_player_by_location |>
      filter(player_name == input$player_select) |>
      dplyr::select(player_name, skill_subtype, avg_pass_rating) |>
      arrange(desc(avg_pass_rating)) |>
      rename(Player = player_name, Location = skill_subtype, `Avg Pass Rating` = avg_pass_rating)
  }, digits = 3)
  
  output$overall_leaderboard <- renderTable({
    req(player_totals())
    player_totals() |>
      arrange(desc(overall_avg_rating)) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_name, team, total_passes, overall_avg_rating) |>
      rename(Player = player_name, Team = team, `Total Passes` = total_passes, `Overall Avg Rating` = overall_avg_rating)
  }, digits = 3)
  
  # ---------------------------------------------------------
  # TAB 2 OUTPUTS
  # ---------------------------------------------------------
  
  output$overall_point_win_pct <- renderTable({
    req(pass_rating_point_wol())
    
    pass_rating_point_wol() |>
      group_by(pass_rating) |>
      summarize(
        total_passes = n(),
        points_won = sum(won_point, na.rm = TRUE),
        win_pct = round((points_won / total_passes) * 100, 2),
        .groups = "drop"
      ) |>
      mutate(win_pct = paste0(win_pct, "%")) |> 
      rename(`Pass Rating` = pass_rating, `Total Passes` = total_passes, 
             `Points Won` = points_won, `% Chance of Winning Point` = win_pct)
  })
  
  output$team_point_win_header <- renderText({
    req(input$team_select)
    paste(input$team_select, "- % Chance to Win Point")
  })
  
  output$team_point_win_pct <- renderTable({
    req(pass_rating_point_wol(), input$team_select)
    
    pass_rating_point_wol() |>
      filter(team == input$team_select) |>
      group_by(pass_rating) |>
      summarize(
        total_passes = n(),
        points_won = sum(won_point, na.rm = TRUE),
        win_pct = round((points_won / total_passes) * 100, 2),
        .groups = "drop"
      ) |>
      mutate(win_pct = paste0(win_pct, "%")) |>
      rename(`Pass Rating` = pass_rating, `Total Passes` = total_passes, 
             `Points Won` = points_won, `% Chance of Winning Point` = win_pct)
  })
  
  # ---------------------------------------------------------
  # TAB 3 OUTPUTS
  # ---------------------------------------------------------
  
  output$oss_team_header <- renderText({
    req(input$oss_team_select)
    paste(input$oss_team_select, "Offensive Strength")
  })
  
  output$oss_team_table <- renderTable({
    req(oss_data(), input$oss_team_select)
    
    oss_data() |>
      filter(team == input$oss_team_select) |>
      arrange(desc(OSS)) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_number, player_name, total_hits, OSS) |>
      rename(`Number` = player_number, Player = player_name, `Total Hits` = total_hits)
  }, digits = 3)
  
  output$oss_overall_table <- renderTable({
    req(oss_data())
    
    oss_data() |>
      arrange(desc(OSS)) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_name, team, total_hits, OSS) |>
      rename(Player = player_name, Team = team, `Total Hits` = total_hits)
  }, digits = 3)
  
  # ---------------------------------------------------------
  # TAB 4 OUTPUTS (OOS)
  # ---------------------------------------------------------
  
  output$oos_header <- renderText({
    req(input$oos_team_select)
    paste(input$oos_team_select, "- Setter to Hitter Efficiency")
  })
  
  output$oos_table <- renderTable({
    req(oos_data(), input$oos_team_select)
    
    oos_data() |>
      filter(team == input$oos_team_select) |>
      arrange(desc(number_sets)) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, Set_player_number, Set_player_name, number_sets, hitter_efficiency) |>
      rename(`Number` = Set_player_number, Player = Set_player_name,
             `Total Sets Given` = number_sets, `Hitter Efficiency` = hitter_efficiency)
  }, digits = 3)

  # ---------------------------------------------------------
  # TAB 5: SERVING DATA PREP
  # ---------------------------------------------------------

  # All serves with SPI components (Ace +1, Good Pressure +0.5, Error -1)
  serve_base <- reactive({
    req(exists("all_matches_outcomes", envir = .GlobalEnv))

    all_matches_outcomes |>
      filter(skill == "Serve") |>
      mutate(
        zone = start_zone,
        ace = evaluation_code == "#",
        good_pressure = evaluation_code == "+",
        error = evaluation_code == "-",
        SPI = (ace * 1.0) + (good_pressure * 0.5) - (error * 1.0)
      )
  })

  # Per-player SPI (min 20 serves)
  serve_player_data <- reactive({
    req(serve_base())

    serve_base() |>
      group_by(team, player_number, player_name) |>
      summarize(
        total_serves = n(),
        SPI = mean(SPI, na.rm = TRUE),
        ace_rate = mean(ace, na.rm = TRUE),
        error_rate = mean(error, na.rm = TRUE),
        .groups = "drop"
      ) |>
      filter(total_serves >= 20)
  })

  # Per-zone SPI for the selected team
  serve_zone_data <- reactive({
    req(serve_base(), input$serve_team_select)

    serve_base() |>
      filter(team == input$serve_team_select, !is.na(zone)) |>
      group_by(zone) |>
      summarize(
        serves = n(),
        SPI = mean(SPI, na.rm = TRUE),
        ace_rate = mean(ace, na.rm = TRUE),
        error_rate = mean(error, na.rm = TRUE),
        .groups = "drop"
      )
  })

  observe({
    req(serve_player_data())
    updateSelectInput(session, "serve_team_select", choices = sort(unique(serve_player_data()$team)))
  })

  # ---------------------------------------------------------
  # TAB 5 OUTPUTS
  # ---------------------------------------------------------

  output$serve_team_header <- renderText({
    req(input$serve_team_select)
    paste(input$serve_team_select, "- Server SPI Leaderboard")
  })

  output$serve_team_table <- renderTable({
    req(serve_player_data(), input$serve_team_select)

    serve_player_data() |>
      filter(team == input$serve_team_select) |>
      arrange(desc(SPI)) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_number, player_name, total_serves, SPI, ace_rate, error_rate) |>
      rename(`Number` = player_number, Player = player_name, `Total Serves` = total_serves,
             `Ace Rate` = ace_rate, `Error Rate` = error_rate)
  }, digits = 3)

  output$serve_overall_table <- renderTable({
    req(serve_player_data())

    serve_player_data() |>
      arrange(desc(SPI)) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_name, team, total_serves, SPI, ace_rate, error_rate) |>
      rename(Player = player_name, Team = team, `Total Serves` = total_serves,
             `Ace Rate` = ace_rate, `Error Rate` = error_rate)
  }, digits = 3)

  output$serve_zone_header <- renderText({
    req(input$serve_team_select)
    paste(input$serve_team_select, "- SPI by Serve Zone")
  })

  output$serve_zone_table <- renderTable({
    req(serve_zone_data())

    serve_zone_data() |>
      arrange(desc(SPI)) |>
      mutate(zone = as.character(zone)) |>
      rename(Zone = zone, Serves = serves, `Ace Rate` = ace_rate, `Error Rate` = error_rate)
  }, digits = 3)

  output$serve_zone_plot <- renderPlot({
    req(serve_zone_data())

    ggplot(serve_zone_data(), aes(x = factor(zone), y = SPI, fill = SPI)) +
      geom_col() +
      labs(x = "Serve Zone", y = "SPI",
           title = paste(input$serve_team_select, "- SPI by Serve Zone")) +
      theme_minimal()
  })

  # ---------------------------------------------------------
  # TAB 6: BLOCKING DATA PREP
  # ---------------------------------------------------------

  # All blocks with Block Influence Score (BIS) components
  block_base <- reactive({
    req(exists("all_matches_outcomes", envir = .GlobalEnv))

    all_matches_outcomes |>
      filter(skill == "Block") |>
      mutate(
        BIS_score = case_when(
          evaluation_code == "#" ~ 1,     # block kill
          evaluation_code == "+" ~ 0.5,   # block touch
          evaluation_code == "-" ~ -1,    # block error
          TRUE ~ 0
        )
      )
  })

  # Per-player blocking stats (min 10 attempts)
  block_player_data <- reactive({
    req(block_base())

    block_base() |>
      group_by(team, player_number, player_name) |>
      summarize(
        attempts = n(),
        kills = sum(evaluation == "Winning block", na.rm = TRUE),
        errors = sum(evaluation == "Error", na.rm = TRUE),
        efficiency = (kills - errors) / attempts,
        touch_rate = mean(evaluation %in% c("Winning block", "In play"), na.rm = TRUE),
        blocks_per_set = sum(evaluation == "Winning block", na.rm = TRUE) / n_distinct(match_id, set_number),
        BIS = mean(BIS_score, na.rm = TRUE),
        .groups = "drop"
      ) |>
      filter(attempts >= 10)
  })

  # Per-team blocking summary
  block_team_data <- reactive({
    req(block_base())

    block_base() |>
      group_by(team) |>
      summarize(
        attempts = n(),
        kills = sum(evaluation == "Winning block", na.rm = TRUE),
        errors = sum(evaluation == "Error", na.rm = TRUE),
        efficiency = (kills - errors) / attempts,
        .groups = "drop"
      ) |>
      arrange(desc(efficiency))
  })

  # Opponent hitting % when a block touch is present in the rally vs not
  block_impact_data <- reactive({
    req(exists("all_matches_outcomes", envir = .GlobalEnv))

    plays_clean <- all_matches_outcomes |> filter(!is.na(skill))

    block_presence <- plays_clean |>
      group_by(match_id, point_id) |>
      summarize(
        block_touch = any(skill == "Block" & evaluation_code %in% c("#", "+")),
        .groups = "drop"
      )

    plays_clean |>
      filter(skill == "Attack") |>
      mutate(kill = evaluation_code == "#", error = evaluation_code == "-") |>
      dplyr::select(match_id, point_id, kill, error) |>
      left_join(block_presence, by = c("match_id", "point_id")) |>
      group_by(block_touch) |>
      summarize(
        kills = sum(kill, na.rm = TRUE),
        errors = sum(error, na.rm = TRUE),
        attempts = n(),
        hitting_pct = (kills - errors) / attempts,
        .groups = "drop"
      )
  })

  # Opponent hitting % for the SELECTED team's blocking:
  # among opponent attacks in matches the team played, split by whether the
  # selected team got a block touch (#/+) in that rally.
  block_impact_team_data <- reactive({
    req(exists("all_matches_outcomes", envir = .GlobalEnv), input$block_team_select)
    sel_team <- input$block_team_select

    plays_clean <- all_matches_outcomes |> filter(!is.na(skill))

    team_matches <- plays_clean |>
      filter(team == sel_team) |>
      distinct(match_id) |>
      pull(match_id)

    team_block_presence <- plays_clean |>
      filter(skill == "Block", team == sel_team) |>
      group_by(match_id, point_id) |>
      summarize(
        block_touch = any(evaluation_code %in% c("#", "+")),
        .groups = "drop"
      )

    opp_attacks <- plays_clean |>
      filter(skill == "Attack", team != sel_team, match_id %in% team_matches) |>
      mutate(kill = evaluation_code == "#", error = evaluation_code == "-") |>
      dplyr::select(match_id, point_id, kill, error) |>
      left_join(team_block_presence, by = c("match_id", "point_id")) |>
      mutate(block_touch = ifelse(is.na(block_touch), FALSE, block_touch))

    by_touch <- opp_attacks |>
      mutate(group = ifelse(block_touch, "Block Touch in Rally", "No Block Touch")) |>
      group_by(group) |>
      summarize(
        kills = sum(kill, na.rm = TRUE),
        errors = sum(error, na.rm = TRUE),
        attempts = n(),
        hitting_pct = (kills - errors) / attempts,
        .groups = "drop"
      )

    overall <- opp_attacks |>
      summarize(
        group = "Overall (All Attacks)",
        kills = sum(kill, na.rm = TRUE),
        errors = sum(error, na.rm = TRUE),
        attempts = n(),
        hitting_pct = (kills - errors) / attempts
      )

    bind_rows(by_touch, overall)
  })

  observe({
    req(block_player_data())
    updateSelectInput(session, "block_team_select", choices = sort(unique(block_player_data()$team)))
  })

  # ---------------------------------------------------------
  # TAB 6 OUTPUTS
  # ---------------------------------------------------------

  output$block_team_header <- renderText({
    req(input$block_team_select)
    paste(input$block_team_select, "- Player Blocking Report")
  })

  output$block_team_table <- renderTable({
    req(block_player_data(), input$block_team_select)

    block_player_data() |>
      filter(team == input$block_team_select) |>
      arrange(desc(BIS)) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_number, player_name, attempts, kills, errors, efficiency, touch_rate, blocks_per_set, BIS) |>
      rename(`Number` = player_number, Player = player_name, Attempts = attempts,
             Kills = kills, Errors = errors, Efficiency = efficiency,
             `Touch Rate` = touch_rate, `Blocks/Set` = blocks_per_set)
  }, digits = 3)

  output$block_overall_table <- renderTable({
    req(block_player_data())

    block_player_data() |>
      arrange(desc(BIS)) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_name, team, attempts, efficiency, touch_rate, BIS) |>
      rename(Player = player_name, Team = team, Attempts = attempts,
             Efficiency = efficiency, `Touch Rate` = touch_rate)
  }, digits = 3)

  output$block_team_summary <- renderTable({
    req(block_team_data())

    block_team_data() |>
      mutate(Rank = row_number()) |>
      relocate(Rank) |>
      rename(Team = team, Attempts = attempts, Kills = kills,
             Errors = errors, Efficiency = efficiency)
  }, digits = 3)

  output$block_impact_table <- renderTable({
    req(block_impact_data())

    block_impact_data() |>
      mutate(block_touch = ifelse(block_touch, "Block Touch in Rally", "No Block Touch")) |>
      arrange(block_touch) |>
      rename(`Block Presence` = block_touch, Kills = kills, Errors = errors,
             Attempts = attempts, `Opponent Hitting %` = hitting_pct)
  }, digits = 3)

  output$block_impact_team_header <- renderText({
    req(input$block_team_select)
    paste(input$block_team_select, "- Opponent Hitting % vs Block Presence")
  })

  output$block_impact_team_table <- renderTable({
    req(block_impact_team_data())

    block_impact_team_data() |>
      rename(`Block Presence` = group, Kills = kills, Errors = errors,
             Attempts = attempts, `Opponent Hitting %` = hitting_pct)
  }, digits = 3)

  output$block_eff_header <- renderText({
    req(input$block_team_select)
    paste(input$block_team_select, "- Blocking Efficiency by Player")
  })

  output$block_eff_plot <- renderPlot({
    req(block_player_data(), input$block_team_select)

    block_player_data() |>
      filter(team == input$block_team_select) |>
      ggplot(aes(x = reorder(player_name, efficiency), y = efficiency, fill = efficiency)) +
      geom_col() +
      coord_flip() +
      labs(x = "Player", y = "Blocking Efficiency",
           title = paste(input$block_team_select, "- Blocking Efficiency")) +
      theme_minimal()
  })

  # =========================================================
  # PRESSURE / CLUTCH DATA PREP
  # "Pressure" = any rally where either team has reached 20 points.
  # =========================================================

  pressure_serves <- reactive({
    req(exists("all_match_data", envir = .GlobalEnv))
    all_match_data |>
      filter(skill == "Serve", home_team_score >= 20 | visiting_team_score >= 20)
  })

  clutch_serve_summary <- reactive({
    req(pressure_serves())
    pressure_serves() |>
      group_by(team, player_name) |>
      summarize(
        total_serves = n(),
        oos_count = sum(evaluation %in% c("Ace", "Positive"), na.rm = TRUE),
        points_won_count = sum(point_won_by == team, na.rm = TRUE),
        errors = sum(evaluation == "Error", na.rm = TRUE),
        .groups = "drop"
      ) |>
      mutate(
        oos_percentage = (oos_count / total_serves) * 100,
        ps_percentage = (points_won_count / total_serves) * 100
      ) |>
      dplyr::select(team, player_name, total_serves, oos_percentage, ps_percentage, errors) |>
      arrange(desc(ps_percentage), desc(total_serves))
  })

  clutch_reception_summary <- reactive({
    req(exists("all_match_data", envir = .GlobalEnv))
    all_match_data |>
      filter(skill == "Reception", home_team_score >= 20 | visiting_team_score >= 20) |>
      group_by(team, player_name) |>
      summarize(
        total_receptions = n(),
        good_passes = sum(evaluation %in% c("Perfect pass", "Positive pass"), na.rm = TRUE),
        side_outs = sum(point_won_by == team, na.rm = TRUE),
        errors = sum(evaluation == "Error", na.rm = TRUE),
        .groups = "drop"
      ) |>
      mutate(
        good_pass_percentage = (good_passes / total_receptions) * 100,
        side_out_percentage = (side_outs / total_receptions) * 100
      ) |>
      dplyr::select(team, player_name, total_receptions, good_pass_percentage, side_out_percentage, errors) |>
      arrange(desc(side_out_percentage), desc(total_receptions))
  })

  clutch_offense_summary <- reactive({
    req(exists("all_match_data", envir = .GlobalEnv))
    all_match_data |>
      filter(skill == "Attack", home_team_score >= 20 | visiting_team_score >= 20) |>
      group_by(team, player_name) |>
      summarize(
        attempts = n(),
        kills = sum(evaluation == "Winning attack", na.rm = TRUE),
        errors = sum(evaluation == "Error", na.rm = TRUE),
        blocked = sum(evaluation == "Blocked", na.rm = TRUE),
        .groups = "drop"
      ) |>
      mutate(
        kill_pct = (kills / attempts) * 100,
        efficiency = (kills - errors - blocked) / attempts
      ) |>
      group_by(team) |>
      mutate(usage_pct = (attempts / sum(attempts)) * 100) |>
      ungroup() |>
      filter(attempts >= 10) |>
      arrange(desc(efficiency))
  })

  total_clutch_leaderboard <- reactive({
    req(clutch_offense_summary(), clutch_serve_summary(), clutch_reception_summary())

    lb <- clutch_offense_summary() |>
      dplyr::select(team, player_name, att_attempts = attempts, att_eff = efficiency) |>
      full_join(
        clutch_serve_summary() |>
          dplyr::select(team, player_name, srv_attempts = total_serves, srv_ps_pct = ps_percentage),
        by = c("team", "player_name")
      ) |>
      full_join(
        clutch_reception_summary() |>
          dplyr::select(team, player_name, rec_attempts = total_receptions, rec_so_pct = side_out_percentage),
        by = c("team", "player_name")
      )

    lb[is.na(lb)] <- 0

    lb |>
      mutate(clutch_index = (att_eff * 100) + rec_so_pct + srv_ps_pct) |>
      filter((att_attempts + srv_attempts + rec_attempts) >= 15) |>
      arrange(desc(clutch_index))
  })

  top_clutch_per_team <- reactive({
    req(total_clutch_leaderboard())
    total_clutch_leaderboard() |>
      group_by(team) |>
      slice_max(clutch_index, n = 1, with_ties = FALSE) |>
      ungroup() |>
      arrange(desc(clutch_index))
  })

  # ---- Serve Efficiency Index (SEI), season-long across all serves ----
  serves_adv <- reactive({
    req(exists("all_match_data", envir = .GlobalEnv))
    all_match_data |>
      filter(skill == "Serve") |>
      mutate(
        serve_type = case_when(
          skill_type == "Jump serve" ~ "Jump",
          skill_type == "Jump-float serve" ~ "Jump-Float",
          skill_type == "Floating serve" ~ "Float",
          TRUE ~ "Other"
        ),
        is_ace = evaluation == "Ace",
        is_error = evaluation == "Error",
        opp_out_of_system = evaluation %in% c("Positive, no attack", "Poor, no attack", "Negative, limited attack"),
        point_won = point_won_by == team
      )
  })

  sei_player <- reactive({
    req(serves_adv())
    serves_adv() |>
      group_by(team, player_name, serve_type) |>
      summarize(
        serves = n(),
        ace_pct = mean(is_ace, na.rm = TRUE) * 100,
        err_pct = mean(is_error, na.rm = TRUE) * 100,
        oos_pct = mean(opp_out_of_system, na.rm = TRUE) * 100,
        win_pct = mean(point_won, na.rm = TRUE) * 100,
        .groups = "drop"
      ) |>
      mutate(sei = (win_pct * 0.5) + (ace_pct * 0.3) + (oos_pct * 0.2) - (err_pct * 0.1)) |>
      filter(serves >= 20) |>
      arrange(desc(sei))
  })

  sei_type_comparison <- reactive({
    req(serves_adv())
    serves_adv() |>
      filter(serve_type %in% c("Float", "Jump", "Jump-Float")) |>
      group_by(serve_type) |>
      summarize(
        `Ace %` = mean(is_ace, na.rm = TRUE) * 100,
        `Error %` = mean(is_error, na.rm = TRUE) * 100,
        `OOS %` = mean(opp_out_of_system, na.rm = TRUE) * 100,
        `Win %` = mean(point_won, na.rm = TRUE) * 100,
        `SEI` = (mean(point_won, na.rm = TRUE) * 50) + (mean(is_ace, na.rm = TRUE) * 30) +
                (mean(opp_out_of_system, na.rm = TRUE) * 20) - (mean(is_error, na.rm = TRUE) * 10),
        .groups = "drop"
      ) |>
      pivot_longer(cols = -serve_type, names_to = "Metric", values_to = "Value")
  })

  # ---------------------------------------------------------
  # DROPDOWN UPDATES
  # ---------------------------------------------------------
  observe({
    req(clutch_serve_summary())
    updateSelectInput(session, "clutch_serve_team", choices = sort(unique(clutch_serve_summary()$team)))
  })
  observe({
    req(clutch_reception_summary())
    updateSelectInput(session, "clutch_rec_team", choices = sort(unique(clutch_reception_summary()$team)))
  })
  observe({
    req(clutch_offense_summary())
    updateSelectInput(session, "clutch_off_team", choices = sort(unique(clutch_offense_summary()$team)))
  })
  observe({
    req(sei_player())
    updateSelectInput(session, "sei_team", choices = sort(unique(sei_player()$team)))
  })

  # ---------------------------------------------------------
  # CLUTCH SERVING OUTPUTS
  # ---------------------------------------------------------
  output$clutch_serve_header <- renderText({
    req(input$clutch_serve_team)
    paste(input$clutch_serve_team, "- Clutch Serving")
  })

  output$clutch_serve_team_table <- renderTable({
    req(clutch_serve_summary(), input$clutch_serve_team)
    clutch_serve_summary() |>
      filter(team == input$clutch_serve_team) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_name, total_serves, oos_percentage, ps_percentage, errors) |>
      rename(Player = player_name, `Total Serves` = total_serves, `Aggressive %` = oos_percentage,
             `Point-Scoring %` = ps_percentage, Errors = errors)
  }, digits = 1)

  output$clutch_serve_overall_table <- renderTable({
    req(clutch_serve_summary())
    clutch_serve_summary() |>
      head(25) |>
      mutate(Rank = row_number()) |>
      relocate(Rank) |>
      rename(Team = team, Player = player_name, `Total Serves` = total_serves,
             `Aggressive %` = oos_percentage, `Point-Scoring %` = ps_percentage, Errors = errors)
  }, digits = 1)

  # ---------------------------------------------------------
  # CLUTCH RECEPTION OUTPUTS
  # ---------------------------------------------------------
  output$clutch_rec_header <- renderText({
    req(input$clutch_rec_team)
    paste(input$clutch_rec_team, "- Clutch Reception")
  })

  output$clutch_rec_team_table <- renderTable({
    req(clutch_reception_summary(), input$clutch_rec_team)
    clutch_reception_summary() |>
      filter(team == input$clutch_rec_team) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_name, total_receptions, good_pass_percentage, side_out_percentage, errors) |>
      rename(Player = player_name, `Total Receptions` = total_receptions,
             `Good Pass %` = good_pass_percentage, `Side-Out %` = side_out_percentage, Errors = errors)
  }, digits = 1)

  output$clutch_rec_overall_table <- renderTable({
    req(clutch_reception_summary())
    clutch_reception_summary() |>
      head(25) |>
      mutate(Rank = row_number()) |>
      relocate(Rank) |>
      rename(Team = team, Player = player_name, `Total Receptions` = total_receptions,
             `Good Pass %` = good_pass_percentage, `Side-Out %` = side_out_percentage, Errors = errors)
  }, digits = 1)

  # ---------------------------------------------------------
  # CLUTCH OFFENSE OUTPUTS
  # ---------------------------------------------------------
  output$clutch_off_header <- renderText({
    req(input$clutch_off_team)
    paste(input$clutch_off_team, "- Clutch Offense")
  })

  output$clutch_off_team_table <- renderTable({
    req(clutch_offense_summary(), input$clutch_off_team)
    clutch_offense_summary() |>
      filter(team == input$clutch_off_team) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_name, attempts, kills, errors, blocked, kill_pct, efficiency, usage_pct) |>
      rename(Player = player_name, Attempts = attempts, Kills = kills, Errors = errors,
             Blocked = blocked, `Kill %` = kill_pct, Efficiency = efficiency, `Usage %` = usage_pct)
  }, digits = 2)

  output$clutch_off_overall_table <- renderTable({
    req(clutch_offense_summary())
    clutch_offense_summary() |>
      head(25) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, team, player_name, attempts, kills, errors, blocked, kill_pct, efficiency, usage_pct) |>
      rename(Team = team, Player = player_name, Attempts = attempts, Kills = kills, Errors = errors,
             Blocked = blocked, `Kill %` = kill_pct, Efficiency = efficiency, `Usage %` = usage_pct)
  }, digits = 2)

  # ---------------------------------------------------------
  # ALL-AROUND CLUTCH OUTPUTS
  # ---------------------------------------------------------
  output$top_clutch_team_table <- renderTable({
    req(top_clutch_per_team())
    top_clutch_per_team() |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, team, player_name, clutch_index, att_eff, rec_so_pct, srv_ps_pct) |>
      rename(Team = team, Player = player_name, `Clutch Index` = clutch_index,
             `Hitting Eff` = att_eff, `Side-Out %` = rec_so_pct, `Serve PS %` = srv_ps_pct)
  }, digits = 2)

  output$clutch_overall_table <- renderTable({
    req(total_clutch_leaderboard())
    total_clutch_leaderboard() |>
      head(20) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, team, player_name, clutch_index, att_eff, rec_so_pct, srv_ps_pct,
                    att_attempts, srv_attempts, rec_attempts) |>
      rename(Team = team, Player = player_name, `Clutch Index` = clutch_index,
             `Hitting Eff` = att_eff, `Side-Out %` = rec_so_pct, `Serve PS %` = srv_ps_pct,
             `Att` = att_attempts, `Srv` = srv_attempts, `Rec` = rec_attempts)
  }, digits = 2)

  # ---------------------------------------------------------
  # SERVE EFFICIENCY (SEI) OUTPUTS
  # ---------------------------------------------------------
  output$sei_team_header <- renderText({
    req(input$sei_team)
    paste(input$sei_team, "- Serve Efficiency Index")
  })

  output$sei_team_table <- renderTable({
    req(sei_player(), input$sei_team)
    sei_player() |>
      filter(team == input$sei_team) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, player_name, serve_type, serves, ace_pct, err_pct, oos_pct, win_pct, sei) |>
      rename(Player = player_name, `Serve Type` = serve_type, Serves = serves,
             `Ace %` = ace_pct, `Error %` = err_pct, `OOS %` = oos_pct, `Win %` = win_pct, SEI = sei)
  }, digits = 1)

  output$sei_overall_table <- renderTable({
    req(sei_player())
    sei_player() |>
      head(15) |>
      mutate(Rank = row_number()) |>
      dplyr::select(Rank, team, player_name, serve_type, serves, ace_pct, err_pct, oos_pct, win_pct, sei) |>
      rename(Team = team, Player = player_name, `Serve Type` = serve_type, Serves = serves,
             `Ace %` = ace_pct, `Error %` = err_pct, `OOS %` = oos_pct, `Win %` = win_pct, SEI = sei)
  }, digits = 1)

  output$sei_type_plot <- renderPlot({
    req(sei_type_comparison())
    ggplot(sei_type_comparison(), aes(x = serve_type, y = Value, fill = serve_type)) +
      geom_col(alpha = 0.85, color = "black") +
      facet_wrap(~Metric, scales = "free_y") +
      scale_fill_brewer(palette = "Set2") +
      labs(title = "Advanced Serve Efficiency: Floaters vs. Jump Serves",
           subtitle = "Season-long averages across all games",
           x = "Serve Style", y = "Score / Percentage", fill = "Style") +
      theme_minimal() +
      theme(strip.text = element_text(face = "bold", size = 12))
  })

  output$sei_quadrant_plot <- renderPlot({
    req(sei_player())
    d <- sei_player() |> filter(serves >= 30)
    req(nrow(d) > 0)

    ggplot(d, aes(x = err_pct, y = oos_pct)) +
      geom_vline(xintercept = mean(d$err_pct), linetype = "dashed", color = "gray50") +
      geom_hline(yintercept = mean(d$oos_pct), linetype = "dashed", color = "gray50") +
      geom_point(aes(color = serve_type, size = serves), alpha = 0.7) +
      scale_color_brewer(palette = "Set1") +
      labs(title = "Interactive Serve Analysis (min 30 serves)",
           x = "Error %", y = "Out-of-System %", color = "Serve Type", size = "Serves") +
      theme_minimal()
  })
}

# Run the application
shinyApp(ui = ui, server = server)

```

